Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers. Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface. Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$. No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces. Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress. The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.

>>>>

As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers. Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface. Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$. No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces. Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress. The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
